### 2024-10-10 LLMs/poster/poster_amld_2020.tex
first results

\usepackage{relsize}		% For \smaller
\usepackage{url}			% For \url
\usepackage{epstopdf}	% Included EPS files automatically converted to PDF to include with pdflatex
\usepackage{moresize}
\usepackage{multicol}
\usepackage[font=small,labelfont=bf]{subcaption} % <-- changed to subcaption
\usepackage{natbib}

\renewcommand{\bibsection}{}

@@

\begin{document}
	\hyphenation{systematic}
\typeout{Poster rendering started}

@@

%%% General Poster Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Eye Catcher, Title, Authors and University Images %%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
%	grid=false,
	columns=3,
	colspacing=4.2mm,
	headerheight=0.08\textheight,
	background=none,
	eyecatcher=false,
	%posterbox options
	headerborder=closed,
	borderColor=black,
	headershape=rectangle,
	headershade=plain,
	headerColorOne=blue,
	textborder=rectangle,
	boxshade=plain,
	boxColorOne=white,
	headerFontColor=white,
	headerfont=\color{white}\large\bfseries\sffamily,
	textfont=\larger\sffamily,
	linewidth=1pt
}
%%% Eye Cacther %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	Eye Catcher, empty if option eyecatcher=false - unused
}
%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\sf\bf
	\vspace{1em}The safe use of LLMs for screening in systematic reviews
}
%%% Authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
 %\url{https://dx.doi.org/10.1038/s41558-019-0684-5}\\

@@

\headerbox{The promise of LLMs}{name=1,column=0,row=0}{

@@

LLMs have appeared useful for various tasks, but how can we \textbf{safely} use them to save work while screening?

\medskip

They are temperamental, and they return text, not probabilites
}

\headerbox{Next token probabilities}{name=2,column=0,row=0, below=1}{

@@

	LLMs are \textbf{probabilistic models}, which calculate the \textbf{probable next token} given a \textbf{prompt}.

	\medskip

	\cite{wang_zero-shot_2024} showed that we can ask a yes/no question and get a probability-like score by subtracting the probability that the next token is no, from the probability it is yes.

	\[
	S(d,t) =
	P(\text{yes}|d,t) - P(\text{no}|d,t)
	\]

	\medskip

	But the paper did not contain a way to use these scores to save work in a way that would reliably satisfy our need in systematic reviews for high recall

@@

\headerbox{Prioritised screening}{name=3,column=0,row=0, below=2}{

@@

	However, if we have probabistic scores for documents, then we can simply do prioritised screening \textit{with} a reliable \textbf{stopping criteria} \citep{callaghan_statistical_2020}
	\smallskip

		\includegraphics[width=\linewidth]{../../figures/stopping.pdf}

@@

\headerbox{Results}{name=21,column=1, span=2, row=0}{
	Using the synergy dataset \citep{de_bruin_synergy_2023}, we compared rankings from LLM screening with rankings generated in a traditional ``active learning'' pipeline with SVMs

	\includegraphics[width=\linewidth]{../../figures/Brouwer_2019.pdf}

	\includegraphics[width=\linewidth]{../../figures/Jeyaraman_2020.pdf}

	The best models mostly, but not always, outperform the baseline
}

\headerbox{Results}{name=22,column=1, span=1, below=21}{

	Llama 3.1 works better than 2 \cite{wang_zero-shot_2024}, and larger models work better than smaller

	\includegraphics[width=\linewidth]{../../figures/macro_comparison.pdf}

\headerbox{Conclusion}{name=32,column=2, span=1, below=21}{

	Performance with 0 human input is impressive. Combining approaches, or using human labels to provide in-context learning could be promising.

\headerbox{Bibliography}{name=bib,column=0,row=0, below=3}{
	\scriptsize

	%\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time_wgb_lp.pdf}
	\bibliographystyle{apalike}
	\bibliography{../LLMs}
}

\begin{posterbox}[name=footerbox,span=2,column=0,above=bottom,boxheaderheight=0em,textborder=none]{}
{
	For more info on stopping criteria see \url{mcallaghan.github.io/buscar-app} \\
	Max Callaghan \\
{\smaller callaghan@mcc-berlin.net, @MaxCallaghan5}
}
\end{posterbox}

>>>>

\usepackage{relsize}		% For \smaller
\usepackage{url}			% For \url
\usepackage{epstopdf}	% Included EPS files automatically converted to PDF to include with pdflatex
\usepackage{moresize}
\usepackage{multicol}
\usepackage[font=small,labelfont=bf]{subcaption} % <-- changed to subcaption

@@

\begin{document}
\typeout{Poster rendering started}

@@

%%% General Poster Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Eye Catcher, Title, Authors and University Images %%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
%	grid=false,
	columns=3,
	colspacing=4.2mm,
	headerheight=0.08\textheight,
	background=none,
	eyecatcher=false,
	%posterbox options
	headerborder=closed,
	borderColor=black,
	headershape=rectangle,
	headershade=plain,
	headerColorOne=blue,
	textborder=rectangle,
	boxshade=plain,
	boxColorOne=white,
	headerFontColor=white,
	headerfont=\color{white}\large\bfseries\sffamily,
	textfont=\larger\sffamily,
	linewidth=1pt
}
%%% Eye Cacther %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	Eye Catcher, empty if option eyecatcher=false - unused
}
%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\sf\bf
	Biased Urns for efficient Stopping Criteria in technology-Assisted Reviews (BUSCAR)
}
%%% Authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
 %\url{https://dx.doi.org/10.1038/s41558-019-0684-5}\\

@@

\headerbox{Problem}{name=problem,column=0,row=0}{

@@

Machine-learning priorised screening can save work, but only if we know when it is \textbf{safe} to stop

	\includegraphics[width=\linewidth]{../pres/images/potential_stopping.pdf}

\headerbox{Urns}{name=urn,column=0,below=problem}{

@@

	The hypergeometric distribution models the likelihood of retrieving $k$ red marbles from an urn containing $N$ marbles, of which $K$ are red, if we pick out $n$ marbles without replacing them.

	\includegraphics[width=\linewidth]{../pres/images/Keats_urn.jpg}

	Thinking of relevant documents as red marbles, this provides a conservative stopping criterion (Callaghan and Müller-Hansen, 2020), when we assume (conservatively) that the likelihood of drawing a red or white marble is equal.

@@

\headerbox{Biased Urns}{name=biasedurn,column=1,span=2,row=0}{

@@

Biased Urn Theory (Fog, 2023), models what happens when the likelihood of drawing a random item of interest is higher than the likelihood of drawing a random irrelevant item. The ratio between these two is the \textbf{bias}
}

\headerbox{Method}{name=method,column=1, span=2, below=biasedurn}{

	\begin{enumerate}
		\item Estimate maximum number of relevant documents in a given confidence interval from random sample
		\item Look back at the last 1/2 of documents since the random sample, and use Wallenius' non-central hypergeometric distribution and Maximum Likelihood Estimation to find the level of bias below which 95\% of the probability distribution occurs
		\item Look back at previous batches (last 1, last 2, last 3...) to see the likelihood of the observed number or relevant documents occuring given the null hypothesis that we have missed our target.
	\end{enumerate}
}

\headerbox{Experiments}{name=exp,column=1, span=2,below=method}{

	We test our stopping criteria with 100 runs on complete systematic review datasets (from Cohen, 2006), with different recall targets (0.8, 0.95, 0.99) and different confidence levels (0.8, 0.95, 0.99). We show the distribution of additional work savings compared to an omniscient criterion, as well as the distribution of recall, both on average, and for each dataset.
}

\headerbox{Results}{name=res,column=1, span=2,below=exp}{

%\setcaptiontype{figure}% Fake a figure environment
%
%	\subfloat[Target recall 0.8 - conf 0.8]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.8_0.8.pdf}}  
%	\hfill
%	\subfloat[Confidence 0.95]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.8_0.95.pdf}}
%	\hfill
%	\subfloat[Confidence 0.99]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.8_0.99.pdf}}
%
%	\subfloat[Target recall 0.95 - conf 0.8]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.95_0.8.pdf}}  
%\hfill
%\subfloat[Confidence 0.95]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.95_0.95.pdf}}
%\hfill
%\subfloat[Confidence 0.99]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.95_0.99.pdf}}
%
%	\subfloat[Target recall 0.99 - conf 0.8]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.99_0.8.pdf}}  
%\hfill
%\subfloat[Confidence 0.95]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.99_0.95.pdf}}
%\hfill
%\subfloat[Confidence 0.99]{
%	\includegraphics[width=0.32\textwidth]{../plots/jp_conservative_bias_0.99_0.99.pdf}}	
%
%  %\caption{Signed distance field representation}

\includegraphics{../plots/composite.pdf}

Using a biased urn results in higher work savings (see example pathway, while still maintaining recall levels above a target level at a given confidence level).

@@

\begin{posterbox}[name=footer,span=2,column=0,above=bottom,boxheaderheight=0em,textborder=none]{}
{
	Email me for how to use the criterion in your project. R and python packages forthcoming. \\
	Max Callaghan \& Finn Müller-Hansen\\
{\smaller callaghan@mcc-berlin.net, @MaxCallaghan5}
}
\end{posterbox}
